### 2015-05-14 corral.tex
fixes

We have implemented two different \texttt{yield} instrumentations in \whoop: \yieldcoarse and \yieldmr.
%
The first instruments \texttt{yield} statements in a binary fashion: if \whoop proves an entry point pair as race free, then it will instrument a \texttt{yield} only after each lock and unlock statement of the pair; else if \whoop finds that a pair might race, then it will instrument a \texttt{yield} after all visible operations of the pair.
%
\yieldmr is a finer-grained instrumentation: it instruments a \texttt{yield} only after each access to a memory region that might race in the pair (regardless if the pair has not been fully proved as race-free), and after each lock and unlock. In our experiments (see \S\ref{evaluation}), \yieldmr significantly outperforms \yieldcoarse.

>>>>

We have implemented two different \texttt{yield} instrumentations in \whoop: \yieldcoarse and \yieldmr.
%
The first instruments \texttt{yield} statements in a binary fashion: if \whoop proves an entry point pair as race free, then it will instrument a \texttt{yield} only after each lock and unlock statement of the pair; else if \whoop finds that a pair might race, then it will instrument a \texttt{yield} after all visible operations of the pair.
%
\yieldmr is a finer-grained instrumentation: it instruments a \texttt{yield} only after each access to a memory region that might race in the pair (regardless if the pair has not been fully proven as race-free), and after each lock and unlock. In our experiments (see \S\ref{evaluation}), \yieldmr significantly outperforms \yieldcoarse.

### 2015-05-14 whoop.tex
cutting space
fixes

Because a driver is processed by Clang and SMACK during the translation from C to Boogie IVL, significant engineering effort was required to map Boogie-level errors back to original source code locations.

@@

\noindent\textbf{Limitations }
%
As a lockset analyzer, \whoop can be imprecise because a violation of the locking discipline does not always correspond to a real race (e.g.\ when lockfree synchronization is used). \whoop also over-approximates drivers, which can be another source of imprecision. Furthermore, the tool does not check for dynamically created locks or for locks provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently treat interrupt handlers in a special way; we just assume that they can execute concurrently with any entry point. One way to address this is to model interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).

>>>>

@@

\noindent\textbf{Limitations }
%
As a lockset analyzer, \whoop can be imprecise because a violation of the locking discipline does not always correspond to a real race (e.g.\ when lockfree synchronization is used). \whoop also uses over-approximation, which can be another source of imprecision. Furthermore, the tool does not check for dynamically created locks or for locks provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently treat interrupt handlers in a special way; we just assume that they can execute concurrently with any entry point. One way to address this is to model interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).
